Fast and scalable Gaussian process modeling of stellar variability \vspace{-3\baselineskip}

### 2016-10-04 paper/ms.tex
minor notes in outline

\begin{enumerate}
\item Non-parametric modeling of time series with correlated noise using Gaussian processes
\item Assumptions:\\
  a). Stationary noise (although this can be broken).\\
  b). Gaussian
\item Problem: can't handle large datasets - e.g. entire Kepler long-cadence; Spitzer light
   curves; Solar curves; short-cadence.
\item Solution(s):\\
  a). HODLR \citep{Ambikasaran2013,Ambikasaran2016}\\
  b). CARMA (Lorentzian power spectra, but with limitations) \citep{Kelly2014}\\
  c). Tri-diagonal (Press \& Rybicki) \citep{1995PhRvL..74.1060R}
\item Problem: HODLR is tricky to use; CARMA requires certain relations between
  coefficients of Lorentzians (right?); P\&R only works for up to 2 components + white noise
\item Solution: Ambikasaran \citep{Ambikasaran2015} shows how sum of exponential kernels can be solved in order
   $O(N*p^2)$, where p is number of Lorentzians.
\item Generalized Ambikasarn for complex coefficients (Hermitian).
\item Performance:\\
  a). Show $O(N*p^2)$ scaling\\
  b). Show comparison to HODLR.\\
  c). Show comparison to wavelet (ala Carter \& Winn).\\
  d). Compare with CARMA Kallman filter(?).
\item Various methods/formulae:\\
  a). Likelihood computation.\\
  b). Generating GP with particular covariance [yet to solve]. [ ]\\
  c). Inferring particular components.\\
  d). Computing derivatives of GPs (as used in RV methods).\\
  e). Forecasting/interpolating.\\
  f). Inferring confidence intervals.\\
  g). Derivative of likelihood function with respect to kernel parameters.\\
  h). Non-stationary GP (can the coefficients vary with time?).\\
  i). Multi-band (each element of extended matrix becomes a matrix).

\item Generalization to non-stationary noise.
\item Example application: TYC 3559\\
  a). Entire long-cadence 17-quarter Kepler dataset (~65k data points).\\
  b). Analysis of solar data.

>>>>

\begin{enumerate}
\item Non-parametric modeling of time series with correlated noise using Gaussian processes
\item Assumptions:\\
  a). Stationary noise (although this can be broken).\\
  b). Gaussian
\item Problem: can't handle large datasets - e.g. entire Kepler long-cadence; Spitzer light
   curves; Solar curves; short-cadence.
\item Solution(s):\\
  a). HODLR \citep{Ambikasaran2013,Ambikasaran2016}\\
  b). CARMA (Lorentzian power spectra, but with limitations) \citep{Kelly2014}\\
  c). Tri-diagonal (Press \& Rybicki) \citep{1995PhRvL..74.1060R}
\item Problem: HODLR is tricky to use; CARMA requires certain relations between
  coefficients of Lorentzians (right?); P\&R only works for up to 2 components + white noise
\item Solution: Ambikasaran \citep{Ambikasaran2015} shows how sum of exponential kernels can be solved in order
   $O(N*p^2)$, where p is number of Lorentzians.
\item Generalized Ambikasarn for complex coefficients (Hermitian).
\item Performance:\\
  a). Show $O(N*p^2)$ scaling\\
  b). Show comparison to HODLR.\\
  c). Show comparison to wavelet (ala Carter \& Winn).\\
  d). Compare with CARMA Kallman filter(?).
\item Various methods/formulae:\\
  a). Likelihood computation.\\
  b). Generating GP with particular covariance [yet to solve]. [ ]\\
  c). Inferring particular components.\\
  d). TBD Computing derivatives of GPs (as used in RV methods).\\
  e). TBD Forecasting/interpolating.\\
  f). TBD Inferring confidence intervals.\\
  g). Autodiff: Derivative of likelihood function with respect to kernel parameters.\\
  h). TBD Non-stationary GP (can the coefficients vary with time?).\\
  i). TBD Multi-band (each element of extended matrix becomes a matrix).

\item Example application: TYC 3559\\
  a). Entire long-cadence 17-quarter Kepler dataset (~65k data points).\\
  b). Simulated datasets - hyperparameter/PSD inference.\\
  c). Analysis of solar data?
